{\LARGE Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-01-28 Paper/main.tex
Equation correction

\begin{document}
	\title{{\LARGE {\color{red}PLACEHOLDER-TITLE:} Functional Linear Regression in a Scalar-on-Function Setting with Applications to Near-Infrared Spectroscopy}}
	\author{Jonghun Baek, Jakob Juergens, Jonathan Willnow}
	\date{11.02.2022}
	\maketitle
	\vspace{1.5 cm}
	\begin{center}
		Research Module in Econometrics and Statistics \\
		Winter Semester 2021/2022
	\end{center}

@@

	\begin{equation}\label{basis_exp_transf}
		\begin{split}
			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} {\color{red}X(\omega)(s)}\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} c_j  \phi_j(s)\right)} {\color{red}\left(\sum_{k \in \mathcal{L}} d_k(\omega)  \psi_k(s)\right)} \right]\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \sum_{j \in \mathcal{I}} \left[ c_j d_k(\omega)\sum_{k \in \mathcal{L}} \textcolor{teal}{ \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s}\right] + \epsilon(\omega)
			= \alpha + \sum_{j \in \mathcal{I}} \left[c_j d_k(\omega) \sum_{k \in \mathcal{L}}  \textcolor{teal}{Z_{j, k}} \right] + \epsilon(\omega) \\
			& \approx \alpha + \sum_{j = 1}^{J} \left[c_j d_k(\omega) \textcolor{violet}{\sum_{k = 1}^{K}  Z_{j, k}} \right] + \epsilon(\omega)
			= \alpha + \sum_{j = 1}^{J} \left[c_j d_k(\omega)\textcolor{violet}{\tilde{Z}_{j}^{K}} \right] + \epsilon(\omega)	
		\end{split}
	\end{equation}

@@

		$$Y_{1,f} = \langle NIR, f\rangle + Z  \biggl\lbrack\frac{var(\langle NIR, f\rangle)}{0.9} - var(\langle NIR, f\rangle)\biggr\rbrack$$

		$$Y_{2,f} = \langle NIR, f\rangle + Z  \biggl\lbrack\frac{var(\langle NIR, f\rangle)}{0.6} - var(\langle NIR, f\rangle)\biggr\rbrack$$

>>>>

\begin{document}
	\title{{\LARGE Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}}
	\author{Jonghun Baek, Jakob R. Juergens, Jonathan Willnow}
	\date{11.02.2022}
	\maketitle
	\vspace{1.5 cm}
	\begin{center}
		Research Module in Econometrics and Statistics \\
		Winter Semester 2021/2022
	\end{center}

@@

	\begin{equation}\label{basis_exp_transf}
		\begin{split}
			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} {\color{red}X(\omega)(s)}\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} c_j  \phi_j(s)\right)} {\color{red}\left(\sum_{k \in \mathcal{L}} d_k(\omega)  \psi_k(s)\right)} \right]\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \sum_{j \in \mathcal{I}} \left[\sum_{k \in \mathcal{L}} c_j d_k(\omega) \textcolor{teal}{ \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s}\right] + \epsilon(\omega)
			= \alpha + \sum_{j \in \mathcal{I}} \sum_{k \in \mathcal{L}} c_j d_k(\omega)  \textcolor{teal}{Z_{j, k}} + \epsilon(\omega) \\
			& \approx \alpha + \sum_{j = 1}^{J} \sum_{k = 1}^{K} c_j d_k(\omega) \textcolor{violet}{Z_{j, k}}  + \epsilon(\omega)	
		\end{split}
	\end{equation}

@@

		\begin{equation}
			\begin{split}
				Y_{1,f} & = \langle NIR, f\rangle + Z  \biggl\lbrack\frac{var(\langle NIR, f\rangle)}{0.9} - var(\langle NIR, f\rangle)\biggr\rbrack \\
				Y_{2,f} & = \langle NIR, f\rangle + Z  \biggl\lbrack\frac{var(\langle NIR, f\rangle)}{0.6} - var(\langle NIR, f\rangle)\biggr\rbrack
			\end{split}
		\end{equation}
